---
title: "Alcohol vs Seat choice"
author: "Michelle Cervantes"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

It appears as though the back row consumes the most alcohol during the game and the front row consumes the least. The middle row's alcohol consumption is in between the other results.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

Based on this chart, we see that the back rows average of alcoholic drinks is an average of 9.6, the middle rows drink average is 3.2 and the front row is 1.8.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

Based on the data there is a chance of 1 in 10,000 that these results would be all the same again. 
The 0 interval shows that Middle-Front areas are the same based on how much alcohol they consume. The Middle-Back variables are different and so are the Front-Back results. The back row still remains as the highest level of alcohol drinkers.

## Conclusions
Based on the charts above, the back row is drinking nearly 10 times the amount of drinks compared to the front row and approximately 3 times as many drinks than the middle row. Based on the inferential graphs, we can conclude that the Middle and Front row have a relationship consisting of nearly the same results and the Back row shares no relationship with any of the other results. 

